Counting infinitely by Oritatami co-transcriptional folding

### 2019-06-19 paper.tex
begining to write intro

%------------------------------------------------------
	\section{Introduction}
%------------------------------------------------------

@@

\subsubsection{In the zag pass ($\rightarrow$)}
Module F read form the row above H$xc$, and fold into a shape F0, F1.
F$y$ is corresponding to the case where $y = (x + c) mod 2$.
There are no carry propagation and the module L, H, R fold into Lbc, Hn, Rb in this pass.

@@

>>>>

%------------------------------------------------------
	\section{Introduction}
%------------------------------------------------------
Our body consists many proteins which is based on genetic sequence in DNA.
DNA sequence has to be copied in order to make proteins because DNA is in cell nucleus.
It is copied to RNA (and its sequence is called \textit{transcript}) by a RNA polymerase and delivered to out of nucleus.
A transcript consists four types nucleobases A, U, G, and C, and a nucleobase are called \textit{bead}
Moreover, they form hydrogen bonds mainly between A and U, and between G and C, then they begin to form at the same time synthesizing.
Once the bead is fixed after that it can not change the position.

@@

\subsubsection{In the zag pass ($\rightarrow$)}
Module F read form the row above H$xc$, and fold into a shape F0, F1.
F$y$ is corresponding to the case where $y = (x + c)$ mod $2$.
There are no carry propagation and the module L, H, R fold into Lbc, Hn, Rb in this pass.

@@

\subsection{Example of folding}
Let's run an infinite counter from 1 bit width.

\subsubsection{The seed conformation}
